Competition

### 2020-09-24 R/competition wrangling.Rmd
divide by area of donuts

- filter out focal plants where donut goes out of plot. (filter(distance_to_edge > outer_circle_radius))
- Using all years is not estimating density accurately. Focal plants are not moving, but in other years there are neighbors without known coordinates. Solution: only use the three transitions where we know the coords of every plant?  Or assume births and deaths don't change density significantly?

@@

```{r}
# df <- y1p1
# L = 0
# U = 10
# by = 0.5
add_density_cols <- function(df, L, U, by, na_edges = TRUE) {

@@

      #get total number of shoots at every ring
      if (length(d2) > 1) {
        future_map2_dfc(lag(d2)[-1], d2[-1],
                        ~ transmute(
                          focal_df,
                          !!glue("shts_{.x}_{.y}") :=
                            shts * (dist > .x & dist <= .y)
                        )
        ) %>% 
          #excludes focal plant with dist == 0
          summarize(across(everything(), ~sum(., na.rm = TRUE)), .groups = "drop")
      } else {
        # if all the rings go outside the plot, then return an empty row
        tibble_row()
      }
    })

@@

If I want this to be in units of shoots/m^2, then I need to calculate the area of the donut:

$$
A = \pi(U^2 - L^2)
$$
But also, like, truncate that donut if it passes outside of the plot.  I don't know how to do that.

>>>>

- ~~filter out focal plants where donut goes out of plot. (filter(distance_to_edge > outer_circle_radius))~~
- Do I need to divide by area of donut?
- Using all years is not estimating density accurately. Focal plants are not moving, but in other years there are neighbors without known coordinates. Solution: only use the three transitions where we know the coords of every plant?  Or assume births and deaths don't change density significantly?

@@

```{r}
# df <- y1p1
# L = 0
# U = 10
# by = 0.5
add_density_cols <- function(df, L, U, by, na_edges = TRUE, per_area = TRUE) {

@@

      #get total number of shoots at every ring
      if (length(d2) > 1) {
          future_map2_dfc(lag(d2)[-1], d2[-1],
                        ~ transmute(
                          focal_df,
                          !!glue("shts_{.x}_{.y}") :=
                            shts * (dist > .x & dist <= .y)
                        )
        ) %>% 
          #excludes focal plant with dist == 0
          summarize(across(everything(), ~sum(., na.rm = TRUE)), .groups = "drop")

      } else {
        # if all the rings go outside the plot, then return an empty row
        tibble_row()
      }
    })

  if (per_area) {
    # Divide by areas of donuts to get shoots/m^2
    d3 <- d[1:(ncol(df_out) + 1)] #in case largest radii are outside of plot for every plant
    A <- pi * (d3[-1]^2 - lag(d3)[-1]^2) #area of donut
    df_out <- map2_dfc(df_out, A, ~.x/.y) #divide each column by each area
  }

@@
